On the Synchronization Power of the Openflow Data Plane

### 2015-04-12 inband-sync.tex
fixing FlowMod. still working on Bundle

%,a match and an action. 
The standard behavior is that the new flow entry simply replaces an existing one
with exactly the same match, and is installed
in addition to an existing one if the match only
partially overlaps. The latter can result
in inconsistencies, especially if the old and the new rule
have the same priority. \stefan{liron, is this correct?}\liron{a bit not clear, lets talk about this}

@@

@@

The Openflow bundle can be seen as a ``mini-transaction'':
a bundles aggregates multiple control commands (e.g., FlowMod messages)
into one execution, so that either all of the control messages are
processed, or none of them is. In particular, if, for some reason, the
configuration request contained in one of the bundled messages cannot
be processed, all the other requests  are rejected and an error
message is sent to the controller that issued them.
This bundled processing can be, when properly configured, done in a
\emph{packet-atomic} way, so that each packet is processed according
to the switch configuration either \emph{before} or \emph{after} the
request was processed.
If used together with the CHECK\_OVERLAP flag, the bundle command also returns a reason 
if the modification failed: the failed command in the bundle:
a CHECK\_OVERLAP flag can be defined for each command in the bundle.
\liron{these last two sentences are not cleaar}

@@

In the remainder of this paper, we will use the notation 
$\textbf{bundle}\{\;\ldots\;\}$ to refer to represent a
sequence of commands in a bundle.
\stefan{liron: i think the following needs more details $:-)$ :} A bundle will always have the following structure:
it first contains a \emph{send message} to start bundle,
followed by a sequence of messages wrapped in bundle and bundle ID, 
and finally end bundle control message for commit.
A bundle always returns a binary result: \emph{error} or \emph{success}.
\liron{the notion of transaction presented next is confusing considering the bundle just explained}
Concretely, a transaction can represent between two to five switch interactions:
if limited space, Algo 7: read, claim id, read again, transaction, unclaim;
if if unlimited space: alg 6 is unbounded, increase policy ID by one.
transactions = five switch interactions , claim pid (line 5+6) together in bundle => one iteraction less?

>>>>

%,a match and an action. 
The standard behavior is that the new flow entry simply replaces an existing one
with exactly the same match, and is installed
in addition to an existing one if the match only
partially overlaps. The latter can result
in inconsistencies, especially if the old and the new rule
have the same priority.

@@

In this paper, we denote the creation of a \emph{FlowMod} message by calling a function named \emph{FlowMod} with the following interface $FlowMod(match, action, flags)$, where flags are used to activate the CHECK\_OVERLAP feature.

Note that the \emph{FlowMod} message (and flow entries) includes more parameters which we don't utilize in this paper and one should use default values for them in order to implement the described schemes.

@@

The Openflow bundle can be seen as a ``mini-transaction'':
a bundles aggregates multiple control commands (e.g., FlowMod messages)
into one execution, so that either all of the control messages are
processed, or none of them is. In particular, if, for some reason, the
configuration request contained in one of the bundled messages cannot
be processed, all the other requests  are rejected and an error
message is sent to the controller that issued them.
This bundled processing can be, when properly configured, done in a
\emph{packet-atomic} way, so that each packet is processed according
to the switch configuration either \emph{before} or \emph{after} the
request was processed.
If multiple FlowMod messages with the CHECK\_OVERLAP flag are sent as a single bundle, the bundle command also returns a reason 
if the checks failed: the failed command in the bundle.
%:a CHECK\_OVERLAP flag can be defined for each command in the bundle.\liron{these last two sentences are not cleaar}

@@

In the remainder of this paper, we will use the notation 
$\textbf{bundle}\{\;\ldots\;\}$ to refer to represent a
sequence of commands in a bundle.
\stefan{liron: i think the following needs more details $:-)$ :} A bundle will always have the following structure:
it first contains a \emph{create bundle message} to start bundle,
followed by a sequence of messages (e.g., FlowMod) each wrapped in a \emph{add to bundle message} with the bundle ID, 
and finally \emph{commit bundle} control message for commit.
A bundle always returns a binary result: \emph{error} or \emph{success}.

\liron{the notion of transaction presented next is confusing considering the bundle just explained}
Concretely, a transaction can represent between two to five switch interactions:
if limited space, Algo 7: read, claim id, read again, transaction, unclaim;
if if unlimited space: alg 6 is unbounded, increase policy ID by one.
transactions = five switch interactions , claim pid (line 5+6) together in bundle => one iteraction less?
